Leadership across cultures and contexts: an exploratory analysis

### 2020-06-22 leadership_across_cultures_contexts.Rmd
Minor text edits.

<!-- WEIRD PEOPLE PROBLEMS -->
There is now a broad consensus on the importance of data from the full range of human cultural diversity. Since the seminal WEIRD people paper [@henrich_weirdest_2010], many social scientists have endevored to obtain data from "non-WEIRD" populations. Dichotomizing populations and their psychologies and social dynamics as WEIRD or non-WEIRD, however, is a mistake.^[A Google Scholar search for "non-WEIRD" produced over 1000 results.] As anthropology has conclusively demonstrated, there is enormous diversity across societies that does not remotely resemble a dichotomy.

Anthropology, on the other hand, has been criticized for exoticizing and essentializing diverse "Others" as part of its colonial history [@said1979; @abu2008]. In this regard, @abu2008 noted that the concept of culture operates much like its predecessor -- race.

@@

There is potentially more diversity within "non-WEIRD" populations as there is within WEIRD ones, and there is also substantial overlap of the behaviors of people everywhere [@brown_human_1991]. @henrich_weirdest_2010 in their critique of the over-reliance on WEIRD samples emphasized a holistic approach to cultural diversity within and across "telescoping" levels of human societies. It is therefore important to assess cultural variation without assuming that everyone within a culture is essentially the same, and without putting undue emphasis on either the between-population differences or similarities.

>>>>

<!-- WEIRD PEOPLE PROBLEMS -->
There is now a broad consensus on the importance of data from the full range of human cultural diversity. Since the seminal WEIRD people paper [@henrich_weirdest_2010], many social scientists have endevored to obtain data from "non-WEIRD" populations. Dichotomizing populations, their psychologies, or social dynamics as WEIRD or non-WEIRD, however, is a mistake.^[A Google Scholar search for "non-WEIRD" produced over 1000 results.] As anthropology has conclusively demonstrated, there is enormous diversity across societies that does not remotely resemble a dichotomy.

Anthropology, on the other hand, has been criticized for essentializing diverse "Others" as part of its colonial history [@said1979; @abu2008]. In this regard, @abu2008 noted that the concept of culture operates much like its predecessor -- race.

@@

There is potentially more diversity within "non-WEIRD" populations than within WEIRD ones, and there is also substantial overlap of the behaviors of people everywhere [@brown_human_1991]. @henrich_weirdest_2010 in their critique of the over-reliance on WEIRD samples emphasized a holistic approach to cultural diversity within and across "telescoping" levels of human societies. It is therefore important to assess cultural variation without assuming that within a population all members are essentially similar, and without putting undue emphasis on either the between-population differences or similarities.
